A Dependently Typed Multi-Stage Calculus \ifnotanonymous\thanks{Supported by organization x.}\fi

### 2019-06-11 main.tex
Finish section 4.

Any reduction sequences from one typed term converge.
Because we have proved Strong Normalization, we can use Newman's Lemma to prove Confluence.
\begin{theorem}[Confluence]
	For any term $M$, if $M \longrightarrow^* M'$ and $M \longrightarrow^* M''$ then
	there exists $M'''$ that satisfies $M' \longrightarrow^* M'''$ and $M'' \longrightarrow^* M'''$.
\end{theorem}

@@

Every typed term is a value or can be reduced to another typed term.
\begin{theorem}[Progress]
	If $x:\tau @\epsilon \notin \G$ and $\G \V M : \tau  @ A$ then
	$ M \in V^A $ or $M'$ exists such that $M \longrightarrow M'$.
\end{theorem}

@@

For every typed term, we can find just one redex to reduce by the evaluation context or it is a value.
This theorem is important because it ensure 
that the evaluation context decides a redex to reduce deterministically.
Specifically, this theorem guarantee that 
when you write a interpreter using the evaluation context of \LMD,
your interpreter works just as intended.

>>>>

Confluence is a property that any reduction sequences from one typed term converge.
Because we have proved Strong Normalization, we can use Newman's Lemma to prove Confluence.

\begin{theorem}[Confluence]
	For any term $M$, if $M \longrightarrow^* M'$ and $M \longrightarrow^* M''$ then
	there exists $M'''$ that satisfies $M' \longrightarrow^* M'''$ and $M'' \longrightarrow^* M'''$.
\end{theorem}

@@

Unique Decomposition ensure that
,for every typed term, we can find just one redex to reduce by the evaluation context or it is a value.
This theorem is important because it guarantee
that the evaluation context decides a redex to reduce deterministically.
Specifically speaking, this theorem guarantee that 
when you write a interpreter using the evaluation context of \LMD,
your interpreter works just as intended.

@@

Progress states $\longrightarrow_s$ defines appropriate reduction for typed terms of \LMD.
Thanks to Unique Decomposition, we can prove this theorem easily.

\begin{theorem}[Progress]
	If $x:\tau @\epsilon \notin \G$ and $\G \V M : \tau  @ A$ then
	$ M \in V^A $ or $M'$ exists such that $M \longrightarrow_s M'$.
\end{theorem}
